Error-Centric Annotation of Learner Corpora

### 2009-04-08 text/paper.tex

\documentclass[12pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage{aleks}
\author{Magdalena Leshtanska \and Aleksandar Dimitrov}
\title{Error-Centric Annotation of Learner Corpora}
\begin{document}
\maketitle
\tableofcontents
\abstract{I am an abstract!}
\section{Introduction}\label{sec:intro}

@@

@@

\section{Conclusion}\label{sec:results}

@@

>>>>

\documentclass{scrartcl}
\usepackage[utf8x]{inputenc}
\usepackage{aleks}
\author{Magdalena Leshtanska \and Aleksandar Dimitrov}
\title{Error-Centric Annotation of Learner Corpora}
\begin{document}
\maketitle
\tableofcontents
\abstract{I am an abstract!}
\section{Introduction}\label{sec:intro}

@@

[Follows information about triggers, and how the play into this general scheme ]

@@

\section{Assessment}\label{sec:results}

@@

\subsection{Quantificational Analysis}

\begin{table}
  \centering
\begin{tabular}{r|c|c}
  Total: & (905,933)& (98.69\%,101.74\%)\\\hline
  $io \wedge iy \wedge ir$:& 438 & 47.76 \%\\
  $so \wedge iy \wedge ir$:& 448 & 48.85 \%\\
  $io \wedge sy \wedge ir$:& 447 & 48.74 \%\\
  $io \wedge iy \wedge sr$:& 480 & 52.34 \%\\
  $so \wedge sy \wedge ir$:& 476 & 51.90 \%\\
  $io \wedge sy \wedge sr$:& 503 & 54.85 \%\\
  $so \wedge iy \wedge sr$:& 499 & 54.41 \%\\
  $so \wedge sy \wedge sr$:& 544 & 59.32 \%\\
  $     io \wedge iy$:& 486      & 52.99 \%\\
  $     so \wedge iy$:& 506      & 55.17 \%\\
  $     io \wedge sy$:& 509      & 55.50 \%\\
  $     so \wedge sy$:& 551      & 60.08 \%\\
  $     io \wedge ir$:& 525      & 57.25 \%\\
  $     so \wedge ir$:& 578      & 63.03 \%\\
  $     io \wedge sr$:& 623      & 67.93 \%\\
  $     so \wedge sr$:& 719      & 78.40 \%\\
  $          io$:& 629           & 68.59 \%\\
  $          so$:& 730           & 79.60 \%\\
\end{tabular}
\caption{Absolute amount of annotation overlap.}\label{tab:1}

\end{table}

Table \ref{tab:1} shows the total amount of corresponding data in the individual
markup. The table's labeling reads as follows: $s$ stands for a non-empty
intersection (or prefix relation for the error types) and $i$ for equality.
$o,y,r$ denote the data type: $o$ stands for error tOkens, $y$ for the error's
tYpe, and $r$ for the errors context (or \textit{tRigger}). Thus, $so\wedge
sy\wedge ir$ is the number of all annotations that have a partial overlap on the
error tokens $E$, a prefix match on the error type $\theta$, and identical error
context.
